\documentclass[12pt]{article}

\usepackage[a4paper, left=2cm, right=2cm, top=2cm]{geometry}

\title{GDD Bevy Survivor}

\begin{document}


\maketitle
\newpage

\tableofcontents
\section{Introduction}

\newpage
\section{Enemies}
What are the key features of enemies and how do they differ to each other.

\begin{itemize}
    \item Movement 
    \item Damage
    \item Health 
    \item Resistance
\end{itemize}

The following subsections describe the different types of enemies. 
\subsection{Walker}
The Walker enemy is the typical “filler” enemy:
\begin{itemize}
    \item Movement: Walks slower than the player in his direction. 
    \item Damage: Deals damage on collision with the player. 
    \item Health: Moderate amount of health. This type should be the cannon fodder. 
    \item Resistance: No specific resistances.
\end{itemize}

\subsection{Sprinter}
The Sprinter enemy is a special type of enemy, which is not as common as the walker type. 
\begin{itemize}
    \item Movement: Keeps distance to player and sprints to the player. 
    \item Damage: Deals damage on collision with the player and knocks him back. 
    \item Health: Moderate amount of health
    \item Resistance: Is “unstoppable” while sprinting.
\end{itemize}

\subsection{Jumper}
The Jumper enemy is a special type of enemy, which is not as common as the walker type.
\begin{itemize}
    \item Movement: Keeps distance to player and jumps to the player. 
    \item Damage: Deals damage on impact and creates a zone with special effect \\
    (slow, poison, fire ...).
    \item Health: Should feel tanky.
    \item Resistance: No specific resistances.
\end{itemize}

\subsection{Shooter}
The Shooter enemy is a special type of enemy, which is not as common as the walker type.
\begin{itemize}
    \item Movement: Keeps distance to the player.  
    \item Damage: Deals damage if projectile hits player. 
    \item Health: Should feel squishy.
    \item Resistance: No specific resistances.
\end{itemize}

\subsection{Swarm}
The Swarm enemy/enemies are a group of enemies. 
\begin{itemize}
    \item Movement: Moves as group from one end to the other. 
    \item Damage: Deals damage on collision with player.
    \item Health: Single enemies of the swarm are very squishy. 
    \item Resistance: Very easy to knock back. 
\end{itemize}
Is a very hard copy of Vampiere-Survivor... 

\subsection{Elite/Minibosses}
Special enemies which are rare and drop special loot. 
Do we want this? 

\subsection{Bosses}
Special enemy which have a mechanic and multiple gimmicks.
Do we want this? 

\subsection{Discussion}
Enemies of the same type can still have different states like: Movement speed, Damage, Health and special shots / effects. 
Each enemy type probably needs its own systems for movement, abilities, take and deal damage, ... .  
How do we want to spawn enemies, how do we handle different waves etc.? 


\newpage
\section{Spells}



\end{document}